---
title: "Exam Presentation"
author: "Group 5"
date: "11th May 2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Outline
### Introduction
- Presentation of data

### Materials and Methods
- Data transforming
- Data visualization
- Logistic regression
- Principal Component Analysis
- K-means clustering

### Results

### Discussion


# Introduction

## Introduction | Introduction
- Byar & Greene prostate cancer data, from Andrews DF and Herzberg AM (1985) 
- Compare four different treatments
- 502 observations of 18 variables

## Introduction | Variables in the data set

Presentation of the variables with a R output or picture?

```{r, echo = TRUE}

```


# Materials and Methods

## Data transforming

## Data visualization | Pre-treatment variables

Plot 1
```{r}

```

## Data visualization | Pre-treatment variables

Plot 2
```{r}

```

## Data visualization | Pre-treatment variables

Plot 3
```{r}

```

## Data visualization | Treatment and outcome

Plot 5A + 5B


## Logistic regression
### 

## Principal Component Analysis
### 

## K-means clustering
### 






##  Output slide
### Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Results
### Results 

```{r pressure}
plot(pressure)
```


